---
title: 'DS 202: Lab 2'
author: "MyTien Kien; kmytien"
date: "2/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r chocolate}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

**1.** How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r plots0}
hist(choco$Rating, xlab = 'Rating')
```

Shown here in the histogram, there are many outliers in the chocolate's ratings. Most of these outliers are ratings of 1.0 to 2.0. Another thing about this histogram is that it's skewed heavily to the left.

```{r plot1}
boxplot(choco$Rating, main = 'Boxplot of Choco Ratings')
```

Shown here in the boxplot diagram, it shows that the median of all chocolate ratings are between 3.0 and 3.5. The outliers are also shown here, showing four outliers of 1.0, 1.5, 1.75 and 2.0. It shows the range being 2.25 to 4.0 (with the exception of the outliers).


**2.** How does the number of ratings depend on the location of the company? Draw a bar chart of the number of reports.
```{r plot3}
barplot(table(choco$Location), las = 2, cex.names = 0.5)
```

From this barplot, I think the more developed/populated the country/location, the higher amount of ratings there are.


**3.** Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.
```{r plot4}
cor(choco$Cocoa_Percent, choco$Rating)
summary(choco[c("Cocoa_Percent", "Rating")])

boxplot(choco$Cocoa_Percent)
rate <- choco[c("Cocoa_Percent", "Rating")]
str(rate)
```

From these functions