---
title: 'DS 202: Lab 2'
author: "MyTien Kien; kmytien, Tanner Dunn; tcdunn "
date: "2/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

```{r chocolate}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

**1.** How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r plots0}
hist(choco$Rating, xlab = 'Rating')
```

Shown here in the histogram, there are many outliers in the chocolate's ratings. Most of these outliers are ratings of 1.0 to 2.0. Another thing about this histogram is that it's skewed heavily to the left.

```{r plot1}
boxplot(choco$Rating, main = 'Boxplot of Choco Ratings')
```

Shown here in the boxplot diagram, it shows that the median of all chocolate ratings are between 3.0 and 3.5. The outliers are also shown here, showing four outliers of 1.0, 1.5, 1.75 and 2.0. It shows the range being 2.25 to 4.0 (with the exception of the outliers).


**2.** How does the number of ratings depend on the location of the company? Draw a bar chart of the number of reports.
```{r plot3}
barplot(table(choco$Location), las = 2, cex.names = 0.5)
```

From this barplot, I think the more developed/populated the country/location, the higher amount of ratings there are.


**3.** Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.
```{r plot4}
cor(choco$Cocoa_Percent, choco$Rating)
summary(choco[c("Cocoa_Percent", "Rating")])
plot(choco$Rating, choco$Cocoa_Percent, xlab = 'Rating', ylab = 'Cocoa Percent')
```

From these functions, we noticed that Cocoa_Percent and Rating do not have any correlation at all. The correlation number is very close to zero, meaning that ratings depend very little to nothing at all on Cocoa_Percent.

**4.** How do different bean origins compare in terms of the flavor of chocolates? Are beans from some places better than the other? Create both numerical and graphical summaries, and explain.
```{r plot5}
#Print out the top 30 Ratings of bean origins
origin_ratings <- aggregate(Rating ~ Bean_Origin, data = choco, FUN= max)
head(origin_ratings[order(-origin_ratings$Rating),], n = 30)

#group by origin
origin <- group_by(choco, choco$Bean_Origin)
#get the average ratings and count
origin1 <- summarise(origin, ave_rating = mean(Rating, na.rm=TRUE), count = n())
#filter out all of the places that only had one rating (there were a lot)
origin2 <- filter(origin1, count>1)
plot(x=factor(origin2$`choco$Bean_Origin`), y=origin2$ave_rating, las = 2, ylab = 'Average Rating', xlab = 'Bean Origin', main = "Average Rating of Bean Origins")
#barplot(origin2$ave_rating ~ origin2$`choco$Bean_Origin`, las = 2, ylab = 'Average Rating', xlab = 'Bean Origin')
```

From the numerical data looking at the top rated bean origin's ratings you can see the 24 bean origin's that have
produced a rating of 4.0 which is the highest. Then we decided to graph the mean rating's of Bean_Origin. There isn't a ton of variability but Tobago stand out with the highest mean. In conclusion a bean's origin does not seem to have a big impact on the chocolate's rating.

**5.** Brainstorm two analyses you would like to perform (with your teammates). Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.
```{r plot6}
above70 <- choco[choco$Cocoa_Percent >= '70%', ]
below70 <- choco[choco$Cocoa_Percent < '70%', ]
mean(above70$Rating)
mean(below70$Rating)
barplot(table(above70$Rating), xlab = 'Rating', ylab = 'Entries with >= 70% Cocoa', main = 'Ratings of Chocolates with 70%+ Cocoa')
barplot(table(below70$Rating), xlab = 'Rating', ylab = 'Entries with < 70% Cocoa', main = 'Ratings of Chocolates with <70%Cocoa')
```
For the first analysis, we wanted to see how much of an effect Cocoa Percent had on taste of chocolate. We saw that a lot of chocolates had 70% cocoa, and decided to split the data into two categories, 70% and above & below 70%. We saw that both had a Rating mean of around 3.2, but chocolates with below 70% cocoa had the higher rating. Although one had the higher average rating, we felt like cocoa percent didn't have too much of an effect on taste.

```{r plot7}
CRatings <- group_by(choco, choco$Company)
CRatings2 <- summarise(CRatings, Comp_Rating = mean(Rating, na.rm=TRUE))
CRatings3 <- head(order(factor(CRatings2$Comp_Rating), decreasing = TRUE), n = 10)
plot(x=factor(CRatings2$`choco$Company`), y=CRatings2$Comp_Rating, las = 2, ylab = 'Ratings', xlab = 'Company', main = 'Companies Average Rating')
choco$Company[CRatings3]
```
The next thing we wanted to see was what Company has the highest average rating. Before printing out the graph we didn't realize there was over 500 companies so seeing the highest rated ones was a bit difficult. So we decided to also print out the top 10. The highest average rated company is the "Chocolate Makers".